R Notebook

### 2019-09-09 src/paper2_maxent_avec_xvalidation.Rmd
update to p2 with auto folder creation

this dataset contains a lot of columns you don't need for the maxent models. Remove them here

@@

select mont
```{r month of interest -change}
mthna <- "jan"
mthno <- "1"
```

@@

```{r train and test inc AIC for reg val}
modelmonth <- cbind(paste0(mthna ,unique(prback$year)))
#modelmonth <- "jan2003"
aicetc <- read.csv("../data/env/AICcCalculations_p2.csv", header = TRUE) #pre-created csv file
betavallist <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(betavallist$regularization)
nfolds <- cbind(c(1:5))

@@

  timeslice <- modelmonth[year] #testing timeslice
  #timeslice <- modelmonth
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(prback, year == yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

  for (h in 1:nrow(betavallist)){
    betamval <-  betavallist[h]
    mod <- maxent(x = train, p = trainpa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("replicates=", nrow(nfolds)), "replicatetype=crossvalidate", paste0("betamultiplier=", betamval)), path = paste0("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxent/p2/models/", timeslice)) #here the full path is needed

@@

for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(prback, year == yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

@@

  mod <- maxent(x = train, p = trainpa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("replicates=", nrow(nfolds)), "replicatetype=crossvalidate", paste0("betamultiplier=", betaval)), path = paste0("C:/Users/bunny/Documents/GitHub/Chapter_1/output/maxent/p2/models/", timeslice)) #here the full path is needed

>>>>

@@

select month
```{r month of interest -change}
mthna <- "mar"
mthno <- "3"
```

@@

```{r train and test inc AIC for reg val}
modelmonth <- cbind(paste0(mthna ,unique(prback$year)))
aicetc <- read.csv("../data/env/AICcCalculations_p2.csv", header = TRUE) #pre-created csv file
betavallist <- read.csv("../data/env/AICcCalculations.csv", header = TRUE) #pre-created csv file
betavallist <- cbind(betavallist$regularization)
nfolds <- cbind(c(1:5))

@@

  timeslice <- modelmonth[year] #testing timeslice
  newf <- paste0("../output/maxent/p2/models/", timeslice)
  dir.create(newf)
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(prback, year == yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

  for (h in 1:nrow(betavallist)){
    betamval <-  betavallist[h]
    mod <- maxent(x = train, p = trainpa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("replicates=", nrow(nfolds)), "replicatetype=crossvalidate", paste0("betamultiplier=", betamval)), path = paste0("../output/maxent/p2/models/", timeslice),"overwrite=true") #here the full path is needed

@@

for (year in 1:nrow(modelmonth)){
  timeslice <- modelmonth[year] #testing timeslice
  newf <- paste0("../output/maxent/p2/models/", timeslice)
  dir.create(newf)
  yr <- str_sub(timeslice, -4) #the year being used for testing
  train <- subset(prback, year == yr) #training data is all years but testing
  trainpa <- train$occurrence #creates a vector of presence/background ID (1/0)
  train  <- subset(train, select = -c(year, occurrence)) #don't need year and occurrence for modelling

@@

  mod <- maxent(x = train, p = trainpa, args=c("maximumiterations=5000", "responsecurves=TRUE", "jackknife=TRUE", "threads=8", "addsamplestobackground=TRUE", paste0("replicates=", nrow(nfolds)), "replicatetype=crossvalidate", paste0("betamultiplier=", betaval)), path = paste0("../output/maxent/p2/models/", timeslice)) #here the full path is needed

### 2019-09-09 src/testing_file.Rmd
update to p2 with auto folder creation

ok new play - try creating an individual netcdf for a month...
```{r}
plst <- list.files("../output/maxent/predictions/testplots/testrasters", full.names = TRUE)

thlst <- list()
anlst <- list()
for (i in 1:length(plst)){
  r <- raster(plst[i])
  aname <- names(r)
  aname <-  str_sub(aname, 13)
  r <- setZ(r, as.numeric(aname), name = "depth")
  thlst[[i]] <- r
  anlst[i] <- aname
}

@@

writeRaster(nstk, "../output/maxent/predictions/testplots/nstk.nc", overwrite = TRUE, format = "CDF", varname = "prob", varunit = "p", longname = "dummy netcdf for hovmollers", xname= "X", yname = "Y", zname = "depth", zunit = "m")
```

>>>>

ok new play - try creating an individual netcdf for a month...
```{r}
plst <- list.files("../output/maxent/predictions/testplots/testrasters", full.names = TRUE)
aea <- raster("../output/env/aea.tif") #the correct CRS
apr <- aea@crs

i = 1

thlst <- list()
anlst <- list()
for (i in 1:length(plst)){
  r <- raster(plst[i])
  aname <- names(r)
  aname <-  str_sub(aname, 13)
  r <- setZ(r, as.numeric(aname), name = "depth")
  crs(r) <- apr
  thlst[[i]] <- r
  anlst[i] <- aname
}

@@

writeRaster(r, "../output/maxent/predictions/testplots/lstk2.nc", overwrite = TRUE, format = "CDF", varname = "prob", varunit = "p", longname = "dummy netcdf for hovmollers", xname= "X", yname = "Y", zname = "depth", zunit = "m")

dirXY <- xyLayer(r, sqrt(x^2 + y^2))
library(zoo)

hovmoller(nstk,
          at = seq(0, 1, .1),
                    interpolate = FALSE,
          par.settings = BuRdTheme)

hovmoller(nstk, ylab ="depth", interpolate = FALSE)

try create empty netcdf

```{r}
data.time <- 3:12 #months

#get depths
dep <- read.csv("../output/maxent/models/apr1998/stackdepthlist_1998.csv", header = TRUE)
dep <- dep$ascdepths

lon <- seq( -999722.7, 1525277, by = 25000)
lat <- seq ( 3538427, -211573.1, by = -25000)

data.distance <- seq(-65,920, by=5)
## Add dimensions and variables which accompany the dimensions (avoided by create_dimvar = FALSE)
dimDepth <- ncdim_def(name='depth', units='m', longname='depth layer', vals=data.distance )
dimTime <- ncdim_def('time', units='month', longname='measurement month', calendar="standard", vals=data.time)

varLat <- ncvar_def(name='lat', units='meters_north', dim=list(lat), missval=NA, longname='lat_m', prec='double')
varLon <- ncvar_def(name='lon', units='meters_east', dim=list(lon), missval=NA, longname='lon_m', prec='double')

varAlt <- ncvar_def(name='depth', units='m', dim=list(dimDepth, dimTime), missval=-9999, longname='depth layer')

vars <- list(varLat, varLon, varAlt)

outputfile <- 'transect.nc'
con <- nc_create(outputfile, vars)
